### 2019-02-25 Sections/quality_of_service.tex
CV QEC

Another approach is to error correct on Gaussian states using non-Gaussian operations\cite{PhysRevA.67.062320}, similar to the entanglement distillation protocol. It is unclear which one is the most advantageous.

>>>>

Another approach is to error correct on Gaussian states using non-Gaussian operations. Such protocols have been proposed \cite{PhysRevA.67.062320} and demonstrated \cite{bib:xiang2010heralded} for entanglement distillation. It has been shown that CV teleportation and distillation based on noiseless amplification can be combined to error correct Gaussian states against Gaussian noise \cite{PhysRevA.84.022339}, implementable using linear optics and photon counting.
However, it is unclear whether such protocolsc can be made fault tolerant.
